Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Re-organised the positive diagnoses in GLAD/EDGI prepan into diagnosis and count columns

```
###Prepan

@@

```{r}

@@

>>>>

```
###Prepan
####Get positive diagnoses

@@

####Merge and clean the data

```{r Combine the positive diagnoses for GLAD/EDGI prepan}

@@

```{r Re-organise the positive diagnosis GLAD/EDGI prepan}

GLAD.prepan_positive_diagnosis_GLADEDGI <- GLAD.prepan_positive_diagnosis_GLADEDGI %>% 
  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)

head(GLAD.prepan_positive_diagnosis_GLADEDGI, 9)
